Deciding Bitvector Termination with Program Synthesis

### 2014-06-23 papers/termination/paper.tex
Change title
Added "soundness, completeness and complexity" section

\title{Synthesising Complex Termination Arguments}

@@

\subsection{Time Complexity}
In Section~\ref{sec:synthesis} we will describe a procedure for solving the synthesis formula.
This procedure has the property that it will find the shortest program meeting the
specification, and as a consequence the runtime of the program synthesiser is dominated
by the size of this shortest program.  To frame the discussion of the runtime of our
termination proving procedure, we first recall the definition of the Kolmogorov complexity
of a function $f$:

>>>>

\title{Deciding Bitvector Termination with Program Synthesis}

@@

\section{Soundness, Completeness and Complexity}
\begin{theorem}
 {\sc Headshot} is sound -- if it says a program terminates then it does.
\end{theorem}

\begin{theorem}
 {\sc Headshot} is complete -- if a program terminates, {\sc Headshot} will find a proof that it does.
\end{theorem}

\begin{theorem}
 {\sc Headshot} is a decision procedure -- it always terminates.
\end{theorem}

\begin{theorem}
 {\sc Kalashnikov} has time complexity $NP^{NP}(K(\sigma))$
\end{theorem}

\begin{theorem}
 {\sc Headshot} uses a single call to {\sc Kalashnikov} and uses an encoding with $O(1)$
 overhead.  It therefore has time complexity $NP^{NP}(K(\tau(P))$ where $\tau(P)$ is the
 termination specification for program $P$.
\end{theorem}

In Section~\ref{sec:synthesis} we will describe a procedure for solving the synthesis formula.
This procedure has the property that it will find the shortest program meeting the
specification, and as a consequence the runtime of the program synthesiser is dominated
by the size of this shortest program.  To frame the discussion of the runtime of our
termination proving procedure, we first recall the definition of the Kolmogorov complexity
of a function $f$:
